The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2016-08-11 paper/mri_paper.tex

This work builds on the investigations of \citeauthor{Umurhan:2007hs} (\citeyear{Umurhan:2007hs}; see also \citei{Umurhan:2007dz}), who first conducted an analytic analysis of the MRI in the weakly nonlinear regime. The present work adds to this foundation both in subject, with our additional analysis of the helical MRI, as well as in scope, with a detailed analysis of MRI saturation properties across parameter space and the comparison of weakly nonlinear analytic work to strongly nonlinear simulation. In particular, we attempt to elucidate the role of boundary layers in the saturation of the MRI, as this is of fundamental importance to laboratory MRI work.

>>>>

In this work we investigate the MRI in the weakly nonlinear regime, where the initial linear growth phase of the instability begins to give way to nonlinear saturation. Weakly nonlinear analysis is a perturbative method for examining a system at marginality. Weakly nonlinear analysis was instrumental in understanding the saturated state of Rayleigh-B\'enard convection (\citei{Newell:1969wr}).

%This work builds on the investigations of \citeauthor{Umurhan:2007hs} (\citeyear{Umurhan:2007hs}; see also \citei{Umurhan:2007dz}), who first conducted an analytic analysis of the MRI in the weakly nonlinear regime. The present work adds to this foundation both in subject, with our additional analysis of the helical MRI, as well as in scope, with a detailed analysis of MRI saturation properties across parameter space and the comparison of weakly nonlinear analytic work to strongly nonlinear simulation. In particular, we attempt to elucidate the role of boundary layers in the saturation of the MRI, as this is of fundamental importance to laboratory MRI work.
